Supplementary Content

### 2022-03-16 experiments/2_supplement/supplement.Rmd
update supplement

Notice that in all three cases, the range of trait variation represented by the strains is the same, even though the number of strains differs (a consequence is that the lower row of panels in Figures \@ref(fig:nine-strain-div), \@ref(fig:three-strain-div), and \@ref(fig:two-strain-div) are identical). This approach allowed us to independently manipulate trait diversity and number of strains.

@@

num_CB_strains <- 3
num_PB_strains <- 3
num_SB_strains <- 3
var_expt <- create_diversity_factorial(
  zero = zero, unity = unity,
  num_div_treatment_levels = num_div_treatment_levels,
  CB_gmax_div = CB_gmax_div, CB_h_div = CB_h_div,
  SB_gmax_div = SB_gmax_div, SB_h_div = SB_h_div,
  PB_gmax_div = PB_gmax_div, PB_h_div = PB_h_div,
  default_9strain = new_strain_parameter(
    n_CB = num_CB_strains,
    n_SB = num_SB_strains,
    n_PB = num_PB_strains,
    values_initial_state =  "bush_ssfig3"
  )
)
display_diversity(4,
  var_expt = var_expt,
  num_CB_strains = num_CB_strains,
  num_SB_strains = num_SB_strains,
  num_PB_strains = num_PB_strains,
  which_graphs = 1
)
```

@@

We also show, in Figure \@ref(fig:growth-rates), the relationship between realised growth rate and the concentration of the respective inhibiting substance, e.g. sulfide for the cyanobacteria. In these graphs only the least and most tolerant strains are shown. The lines cross due to the tradeoff. At high concentrations of the inhibiting substance the more tolerant strain has higher realised growth rate, while at lower concentrations it is the less tolerant strain that has the higher realised growth rate.

@@

```{r repl_meth1, echo=FALSE, eval = TRUE}
repl_meth <- readRDS(here("data", "0_ss_finding", "replication_method", "ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
temp_meth <- readRDS(here("data", "0_ss_finding", "temporal_method", "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
```

@@

@@

@@

```{r ss-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth1)', fig.height=8, fig.width=8, fig.align="center"}
wait_time <- "1e+04"
ss_9s <- readRDS(here(paste0("data", "0_ss_finding", "temporal_method", "ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
#stab_9s <- readRDS(here(paste0("data", "0_ss_finding", "temporal_method", "stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

@@

## SB diversity effect oxic to anoxic transition

>>>>

Notice that in all three cases, the range of trait variation represented by the strains is the same, even though the number of strains differs. This approach allowed us to independently manipulate trait diversity and number of strains. Also note that maximum growth rate of strains is evenly distributed on a log scale, even though it may appear at first site that they are distributed evenly on a linear scale (e.g. Figure \@ref(fig:three-strain-div)).

@@

num_CB_strains <- 3
num_PB_strains <- 3
num_SB_strains <- 3
var_expt <- create_diversity_factorial(
  zero = zero, unity = unity,
  num_div_treatment_levels = num_div_treatment_levels,
  CB_gmax_div = CB_gmax_div, CB_h_div = CB_h_div,
  SB_gmax_div = SB_gmax_div, SB_h_div = SB_h_div,
  PB_gmax_div = PB_gmax_div, PB_h_div = PB_h_div,
  default_9strain = new_strain_parameter(
    n_CB = num_CB_strains,
    n_SB = num_SB_strains,
    n_PB = num_PB_strains,
    values_initial_state =  "bush_ssfig3"
  )
)
display_diversity(4,
  var_expt = var_expt,
  num_CB_strains = num_CB_strains,
  num_SB_strains = num_SB_strains,
  num_PB_strains = num_PB_strains,
  which_graphs = 1
)

#0.05*2^(CB_gmax_div) - 0.05
#0.05 - 0.05*2^(-CB_gmax_div)

@@

A consequence of this variation and of the tradeoffs is shown in  Figure \@ref(fig:growth-rates), which shows the relationship between realised growth rate and the concentration of the respective inhibiting substance, e.g. sulfide for the cyanobacteria. In these graphs only the least and most tolerant strains are shown. The lines cross due to the tradeoff. At high concentrations of the inhibiting substance the more tolerant strain has higher realised growth rate, while at lower concentrations it is the less tolerant strain that has the higher realised growth rate.

@@

```{r repl-meth1, echo=FALSE, eval = TRUE}
repl_meth <- readRDS(here("data", "0_ss_finding", "replication_method", "ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
temp_meth <- readRDS(here("data", "0_ss_finding", "temporal_method", "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
```

@@

### Overal effects of diversity

@@

### An example of stable states

Figure \@ref(fig:repl-meth-ex1) shows an example of stable states along the oxygen diffusivity gradient produced by the replication method for finding stable states. The patterns are similar to those produced by the temporal method for finding the stable states (see Figure 3 in the main report), though differ in one respect: some of the more tolerant strains occur in the stable states found by the temporal method (Figure 3 in the main report), while they do not occur in stable states found by the replication method (Figure \@ref(fig:repl-meth-ex1) here). We understand that the appearance of these strains is transient, and the difference in their appearance in results of the two methods is due to differences in starting conditions of the two methods, and that this difference influences how long transients are present for. Transients close to a state change are likely longer for longer in the temporal method than the replication method.

An interesting feature of these results is that although the position of the oxic to anoxic tipping point is affected by diversity (Figure \@ref(fig:div-repl-meth1) and Figure 3 in the main report) there is no evidence of more tolerant strains being present in the final system state (Figure \@ref(fig:repl-meth-ex1)). This phenomenon is explained in Section \@ref(SB2).

(ref:repl-meth-ex1) Stable states found with the **replication method** with intermediate levels of diversity in all functional groups. Figure features are otherwise the same as those in Figure \@ref(fig:repl-meth2)).

```{r repl-meth-ex1, echo = FALSE,  include=TRUE, fig.cap='(ref:repl-meth-ex1)', fig.height=8, fig.width=8, fig.align="center"}
repl_meth <- readRDS(here("data", "0_ss_finding", "replication_method", "ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
fig_state_vs_o2diff_sidebyside_dots(repl_meth[94,])
```

@@

```{r ss-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth1)', fig.height=8, fig.width=8, fig.align="center"}
wait_time <- "1e+04"
ss_9s <- readRDS(here("data", "0_ss_finding", "temporal_method", paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
#stab_9s <- readRDS(here(paste0("data", "0_ss_finding", "temporal_method", "stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

@@

## SB diversity effect oxic to anoxic transition {#SB2}
